Model checking for simplified Naomi

### 2023-01-15 src/naomi-simple_model-checks/model-checks.Rmd
Thinking a little about how to do model checking

```{r}
#' Yes!
```

>>>>

```{r}
tmb <- readRDS("depends/tmb.rds")

outputs <- tmb$outputs

indicators <- naomi::add_output_labels(outputs) %>%
  left_join(outputs$meta_area %>% select(area_level, area_id, center_x, center_y)) %>%
  sf::st_as_sf()

indicators %>%
  filter(
    age_group == "Y015_049",
    indicator == "prevalence",
    area_level == 4
  ) %>%
  ggplot(aes(fill = mode)) +
  geom_sf() +
  viridis::scale_fill_viridis(labels = scales::percent_format()) +
  naomi::th_map() +
  facet_wrap(~sex)

indicators %>%
  filter(
    age_group == "Y015_049",
    indicator == "prevalence",
    area_level == 4
  ) %>%
  names()
```

Next steps here are:

* Add column to `indicators` with the "raw" value of the indicator
* Add column to `indicators` with the quantile of the raw value within samples from the posterior
* Start outputting `tmb$outputs` for the other inference methods
* Use existing or own functions to produce coverage histograms and ECDF difference plots
